Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit Introduction

\begin{abstract} 
    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These stellar halos are a key fossil record of galaxy assembly history. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. 
    Shallow images and/or over-simplified parametric models cannot capture the extended 
    stellar halo and result in underestimated stellar masses.
    Our extended profiles reveal a number of mass-dependent trends. 
    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
    with stellar mass, but we find no difference in color gradients with mass. 
    As in previous work, we see a clear trend towards more extended outer profiles 
    in more massive galaxies. 
    Thus, when this extended light is not properly accounted for, the stellar mass 
    function is systematically underestimated at the highest masses.
    Our results are broadly consistent with the two phase formation scenario of massive 
    galaxies in which outer envelopes are built up at late times from minor merging. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.
\end{abstract}

@@

    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, 
    Qu2017}). For instance, recent results from the Illustris\footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}). \rachel{Given that Illustris gets the SMF totally wrong at high stellar mass, is there a reason we should be quoting their results?  Perhaps better to wait for Illustris-TNG?  Or give some caveat here that it's not clear that the physics that shapes the most massive galaxies is a realistic implementation?}
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront this model with additional observations,  in particular, the detailed surface mass density profiles of low redshift massive galaxies. Early studies based on one-dimensional light profiles suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g. \citealt{Kormendy2009}; except for the
    most central region) and that the \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). However,  later work revealed a more complicated  situation  showing  that  ETGs  belong to two famillies, those that follow single-\ser{} law, versus those that significant deviation from the single-\ser{} profile \citep{Schombert2015}. \rachel{You should say what differed in these later studies; e.g., use of deeper/better data?} Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).

    Until now,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller sample sizes (e.g cite CLASH AND FRONTIER FIELDS??). In this paper, we take advantage of new high-quality (median  seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in the $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive galaxies out to 100 kpc. The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. We select a large sample (${\sim} 7000$) of massive central galaxies at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions. \rachel{Outline does not mention section 5.}

>>>>

\begin{abstract}

    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These stellar halos are a key fossil record of galaxy assembly history. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. 
    Shallow images and/or over-simplified parametric models cannot capture the extended 
    stellar halo and result in underestimated stellar masses.
    Our extended profiles reveal a number of mass-dependent trends. 
    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
    with stellar mass, but we find no difference in color gradients with mass. 
    As in previous work, we see a clear trend towards more extended outer profiles 
    in more massive galaxies. 
    Thus, when this extended light is not properly accounted for, the stellar mass 
    function is systematically underestimated at the highest masses.
    Our results are broadly consistent with the two phase formation scenario of massive 
    galaxies in which outer envelopes are built up at late times from series of merging
    events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

\end{abstract}

@@

    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total galaxy stellar 
    mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront this model with additional observations, 
    in particular, the detailed surface mass density profiles of low redshift massive 
    galaxies. 
    Early studies based on one-dimensional light profiles suggested that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    However, recently, detailed empirical comparison of surface brightness profiles 
    revealed a more complicated situation showing that ETGs belong to two famillies, 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).

    Until now, studies of the surface brightness or mass density profiles of massive 
    galaxies have been either conducted using large samples but with shallow imaging, 
    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
    Capaccioli2015}). 
    In this paper, we take advantage of new high-quality (median seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
    galaxies out to 100 kpc. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and initial sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass.
    Section \ref{sec:final} summaries the final sample selection procedure. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.
